---
title: "Guide to AutoTransformR"
author: "Alycia Butterworth, Brenden Everitt, Rayce Rossum"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Guide to AutoTransformR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

A common application of supervised machine learning is identifying the object of an image. One issue that users encounter is a model misclassifying a new image because the object is rotated or translated in some way that was not captured in the training images. The purpose of this package is to create a more robust set of images for users to train their model with. The package will accept an image as an input, apply a series of transformations to it, and return an array of transformed pixel values. Transformations include: rotating, mirroring, and translating (shifting the object's location in the frame).

## Functions

### Rotate

Rotates an image the user-specified number of times. The image will be rotated to a random degree of roation in the clockwise direction, with the maximum rotation angle specified by the user. The pixel values of the original and rotated images is returned.

**Function:**

`rotate(image_path, num_images, max_rotation)`

**Arguments:**

- `image_path`: file path of the input image (string)
- `num_images`: number of randomly rotated images to be returned (integer)
- `max_rotation`: maximum allowable degrees of rotation of the images (integer) between 1 and 360

**Output:**

- An array of pixel values of the rotated images. Array contains `num_images` + 1 images (original plus all rotated images)

**Example:**

- `rotate("../tests/testthat/img/milad.jpg", 10, 280)`


### Mirror

Mirrors an image in the horizontal and/or vertical direction and returns the pixel values of the original and mirrored image(s).

**Function:**

`mirror(image_path, direction)`

**Arguments:**

- `image_path`: file path of the input image (string)
- `direction`: direction of mirroring (string, optional) 'horizontal', 'vertical', or 'all'. If not specified, defaults to 'all'

**Output:**

- An array of pixel values of the mirrored images. Array contains 3 images if `direction = 'all'` (original, horizontally mirrored, vertically mirrored) or 2 images if direction is horizontal or vertical (original image, mirrored image)

**Example:**

- `mirror("../tests/testthat/img/milad.jpg", "horizontal")`


### Translate

Translate will move an image within its frame, so that the topic of the image will be shifted to a new location in the frame. The distance and direction of translation will be chosen randomly, but the user specifies the maximum distance of the translation and the number of images they want generated. It returns the pixel values of the original and translated images.

**Function:**

`translate(image_path, num_images, max_translation)`

**Arguments:**

- `image_path`: file path of the input image (string)
- `num_images`: number of randomly translated images to be returned (integer)
- `max_translation`: maximum distance in pixels that the image can be translated (integer)

**Output**

- An array of pixel values of the translated images. Array contains `num_images` + 1 images (original plus all translated images)

**Example:**

- `translate("../tests/testthat/img/milad.jpg", 5, 80)`



## Usage Examples

Perform transformations on the image using the mirror, rotate, and translate functions:

```{r}
library(AutoTransformR)

# mirror function with horizontal and vertical mirroring
m <- mirror("../tests/testthat/img/milad.jpg")

# rotation with 8 rotated images returned and a maximum rotation of 360 degrees
r <- rotate("../tests/testthat/img/milad.jpg", 8, 360)

# translation with 8 translated images returned and a maximum translation of 60 pixels
t <- translate("../tests/testthat/img/milad.jpg", 5, 60)

```

**OUTPUT:**

Use `dim()` to see the dimensions of the returned array.

- first 2 dimensions are the image pixel values
- third dim is rgb color (for coloured images only, this dimension will not exist if the image is fully black and white)
- fourth dimension is the number of photos the array contains

```{r}
dim(m)  # mirror function
```

```{r}
dim(r)  # rotate function
```

```{r}
dim(t)  # translate function
```

**VIEW TRANSFORMED IMAGES:**

To access individual images in the returned array, you must use the last dimension of the array to index to the image in question. The first image in the array is the original, the transformed images follow. Below are examples of how to view the images using the the function `imageshow` from the package `OpenImageR`.

**Original Image:**  

```{r, fig.align='center'}
library(OpenImageR)

# View original image
imageShow(m[,,,1])
```

**Mirrored Image:**  

If the direction of mirroring is "all", the array will have the horizontally mirrored image at index 2, and the vertically mirrored image at index 3.

```{r, fig.align='center'}
# view horizontal mirroring
imageShow(m[,,,2])
```

**Rotated Image:**  

```{r, fig.align='center'}
# view one of the rotated images
imageShow(r[,,,3])
```

**Translated Image:**  

```{r, fig.align='center'}
# view one of the translated images
imageShow(t[,,,2])
```



